It is not hard to encounter the crowded WLANs scenario exemplified in Section~\ref{motivation}. Even nowadays it is not rare to have multiple WiFi devices at home attempting to access the channel at the same time: watching an on-line video stream, surfing the Web, receiving VoIP calls and uploading data from your personal health monitoring device.

CSMA/CA has been the de facto standard for coordinating transmissions in WLANs; nevertheless, its performance degrades when imposing heavy traffic on crowded scenarios like the one proposed above, where tens of devices must coordinate their transmission attempts in a totally distributed manner. This degradation in the system performance can be appreciated in the form of video lags while streaming or in below-average download speeds.

By removing the randomness from CSMA/CA's contention mechanism, the proposed CSMA/ECA achieves a better performance while allowing many nodes to coexist in a collision-free environment. Nevertheless, CSMA/ECA lacks of mechanisms to face different scenarios regarding: Quality of Service (QoS), hidden/exposed node mechanisms, performance against different traffic patterns and contention parameters optimization; which on the other hand have been the focus of study in CSMA/CA for many years.

Although it has proven to best CSMA/CA's throughput in controlled simulation environments, CSMA/ECA is far away from being considered as an amend to the standard and/or be hard-coded in real WNICs.

This work aims at bringing the benefits of CSMA/ECA to home WLANs by means of its implementation on real hardware. Its successful completion will provide a better alternative to CSMA/CA, capable of coping with the strict requirements of future networks and services. Furthermore, it will lay the groundwork for MAC protocol prototyping in cheap commodity hardware following the WMP principle, so anyone in the research community will be able to follow the procedures contained in this work, replicate and further develop MAC technologies.